Reanalysis Step 7: Sample Comparison Table

### 2025-09-04 reanalysis-7-missingness_patterns.qmd
data comparison

# Function to compute summary statistics for categorical variables
summarize_categorical <- function(data, var) {
  tbl <- table(data[[var]], useNA = "ifany")
  props <- prop.table(table(data[[var]], useNA = "no"))

  levels_df <- data.frame(
    variable = paste0(var, "_", names(props)),
    n = as.vector(table(data[[var]], useNA = "no")),
    pct = 100 * as.vector(props)
  )

>>>>

# Function to compute summary statistics for categorical variables
summarize_categorical <- function(data, var) {
  # Check if variable exists in data
  if (!(var %in% names(data))) {
    return(data.frame(
      variable = var,
      n = NA,
      pct = NA,
      n_missing = NA,
      pct_missing = NA
    ))
  }

  # Get table including NA
  tbl <- table(data[[var]], useNA = "no")

  # Handle case where all values are NA or empty
  if (length(tbl) == 0) {
    return(data.frame(
      variable = var,
      n = 0,
      pct = NA,
      n_missing = nrow(data),
      pct_missing = 100
    ))
  }

  # Calculate proportions
  props <- prop.table(tbl)

  # Create data frame with results
  levels_df <- data.frame(
    variable = paste0(var, "_", names(tbl)),
    n = as.vector(tbl),
    pct = 100 * as.vector(props),
    stringsAsFactors = FALSE
  )
